Descriptive stuff

### 2023-05-10 notebook/descriptive.qmd
Add activities models + general framework for brms targets

tar_load(c(survey_orgs, survey_countries, survey_all))
tar_load(c(world_map))

@@

>>>>

tar_load(c(survey_orgs, survey_countries, survey_all))
tar_load(c(world_map))
tar_load(c(summary_activities, models_activities))

@@

## Which issues do these NGOs work on?

```{r plot-issues-worked-on, fig.width=6, fig.height=4}
df_issues_most <- survey_orgs %>%
  group_by(Q3.2.clean, potential.contentiousness) %>%
  summarise(num = n()) %>%
  ungroup() %>%
  arrange(desc(num)) %>%
  mutate(issue = factor(Q3.2.clean, levels = rev(unique(Q3.2.clean)), ordered = TRUE)) %>%
  mutate(prop = num / sum(num), cum.prop = cumsum(prop))

ggplot(df_issues_most, aes(x = num, y = issue, color = potential.contentiousness)) +
  geom_pointrange(aes(xmin = 0, xmax = num)) +
  scale_x_continuous(sec.axis = sec_axis(~ . / sum(df_issues_most$num),
                                         labels = label_percent())) +
  scale_color_manual(values = c(clrs$Prism[2], clrs$Prism[8]), name = NULL) +
  labs(x = "Organizations", y = NULL) +
  theme_ingo() + 
  theme(legend.position = c(1, 0), legend.justification = c(1, 0),
        legend.direction = "horizontal", panel.grid.major.y = element_blank())
```

### What kinds of activities do these NGOs engage in?

```{r plot-activities, fig.width=7, fig.height=4.5}
ggplot(summary_activities$df_activities_collapsed, 
       aes(x = prop, y = fct_rev(response), color = potential.contentiousness)) +
  geom_pointrange(aes(xmin = 0, xmax = prop), position = position_dodge(width = 0.75),
                   size = 0.5) +
  labs(x = "Proportion selected", y = "How often INGO does work") +
  scale_color_manual(values = c(clrs$Prism[2], clrs$Prism[8]), name = NULL,
                     guide = guide_legend(reverse = TRUE)) +
  scale_x_continuous(labels = label_percent()) +
  facet_wrap(~ question, ncol = 2) +
  theme_ingo() + 
  theme(legend.position = c(1, 0), legend.justification = c(1, 0),
        legend.direction = "vertical", strip.text = element_text(size = rel(0.75)),
        panel.grid.major.y = element_blank())
```

```{r tab-activities-contentiousness-diffs}
#| tbl-cap: Median differences in proportion of high and low contention INGOs selecting frequency of type of work. Probability that the proportion is greater than 0 given in parentheses.
models_activities %>% 
  unnest(diffs_summary) %>% 
  mutate(nice_value = glue::glue(
    "{diff}<br>({p})",
    diff = label_number(style_negative = "minus", accuracy = 0.01)(y),
    p = label_number(accuracy = 0.01)(p_greater_0))
  ) %>% 
  ungroup() %>% 
  select(question, response, nice_value) %>% 
  pivot_wider(names_from = "response", values_from = "nice_value") %>% 
  gt() %>%
  fmt_markdown(columns = 2:4) %>%
  cols_align(align = "left", columns = question) %>%
  cols_label(question = "") %>% 
  opts_theme()
```

### Challenges and obstacles to mission

```{r analyze-obstacles}
# df.plot.obstacles.raw <- survey.orgs.clean %>%
#   filter(!is.na(Q3.12_obstacle)) %>%
#   mutate(obstacle = str_split(Q3.12_obstacle, ", ")) %>%
#   unnest(obstacle) %>%
#   mutate(obstacle = recode(obstacle,
#     `access to country` = "bureaucratic, legal, and political",
#     `political context` = "bureaucratic, legal, and political",
#     `bureaucratic and legal` = "bureaucratic, legal, and political"
#   )) %>%
#   group_by(obstacle) %>%
#   summarise(num = n()) %>%
#   arrange(desc(num))
# 
# df.plot.obstacles.denom <- survey.orgs.clean %>%
#   filter(!is.na(Q3.12_obstacle)) %>%
#   nrow()
# 
# df.plot.obstacles <- df.plot.obstacles.raw %>%
#   mutate(prop = num / df.plot.obstacles.denom) %>%
#   mutate(obstacle = capitalize(obstacle)) %>%
#   filter(num > 20, obstacle != "Other") %>%
#   mutate(obstacle = fct_inorder(obstacle))
# 
# plot.obstacles <- ggplot(df.plot.obstacles, aes(x=prop, y=fct_rev(obstacle))) +
#   geom_pointrangeh(aes(xmin=0, xmax=prop)) +
#   scale_x_continuous(labels=scales::percent) +
#   labs(x="Proportion of respondents", y=NULL) +
#   theme_ath() + theme(panel.grid.major.y=element_blank())
# 
# plot.obstacles
# 
# fig.save.cairo(plot.obstacles,
#                filename="3-obstacles",
#                width=4.5, height=2)
```
